Verification of a Deterministic Random Bits Generator

### 2015-12-24 paper/paper.tex
fixed claims about pr and backtracking resistance

\section{Introduction}
A DRBG is a program that takes a source of randomness, or entropy, and stretches it out into a string of pseudorandom bits. \stdtitle{NIST SP 800-90A} \cite{nist} DRBG provides backtracking resistance and, optionally, prediction resistance. Backtracking resistance means that even if the whole (secret) state of the DRBG is known at time $t$, the state at time $t - 1$ cannot be computed. Note that this implies the state at time $t - i$ cannot be computed for all $i \geq 1$. Prediction resistance means that even if the whole (secret) state of the DRBG is known at time $t$, the state at time $t + 1$ cannot be computed. Again, note that this implies the state at time $t + i$ cannot be computed for all $i \geq 1$. Here, “time” is counted in terms of calls to the \lstinline{generate} function.

@@

\subsection{The Update Function}
Before showing any of the public function, I must first define a helper function, the \lstinline{update} function. See \stdtitle{NIST SP 800-90A \S 10.1.2.2} for the corresponding NIST specification. The \lstinline{update} function takes a \lstinline{key}, a \lstinline{value}, and an optional nonce and returns a new \lstinline{key} and a new \lstinline{value}. This function will be called at least once in each of the public functions, and the goal is to provide backtracking resistance. What this means is that the original \lstinline{key} cannot be computed from the new \lstinline{key} (note that the \lstinline{value}(s) is public anyways; see \S \ref{funcgenerate}).

@@

Notice that the backtracking resistance property follows directly from the property of HMAC (that the key cannot be computed).

@@

\subsection{The Reseed Function}
There are times when the DRBG state must be reseeded with new bits of entropy. This can happen because \lstinline{generate} has been called many times with the current bits of entropy, or because prediction resistance is requested. Reseeding with fresh entropy automatically provides prediction resistance, as the state at time $t + 1$ cannot be computed from the state at time $t$ alone - entropy is also needed. Note that reseeding is preferred over simply instantiating a new DRBG state because if the source of entropy fails silently (supposed the bits of entropy returned are not actually random), at least the DRBG still has some randomness left over from the old entropy.

>>>>

\section{Introduction}
A DRBG is a program that takes a source of randomness, or entropy, and stretches it out into a string of pseudorandom bits. \stdtitle{NIST SP 800-90A} \cite{nist} DRBG provides backtracking resistance and, optionally, prediction resistance. Backtracking resistance means that even if the whole (secret) state of the DRBG is known at time $t$, an adversary will not be able to distinguish between a truly random bitstring and a bitstring generated by the DRBG at some time before $t$. Prediction resistance is the complement, providing the same assurance for some time including and after $t$. Here, “time” is counted in terms of calls to the \lstinline{generate} function.

@@

\subsection{The Update Function}
Before showing any of the public function, I must first define a helper function, the \lstinline{update} function. See \stdtitle{NIST SP 800-90A \S 10.1.2.2} for the corresponding NIST specification. The \lstinline{update} function takes a \lstinline{key}, a \lstinline{value}, and an optional nonce and returns a new \lstinline{key} and a new \lstinline{value}. This function will be called at least once in each of the public functions, and the goal is to provide backtracking resistance. This is achieved by having the secret internal state of the DRBG (the \lstinline{key}) be the output of HMAC.

@@

@@

\subsection{The Reseed Function}
There are times when the DRBG state must be reseeded with new bits of entropy. This can happen because \lstinline{generate} has been called many times with the current bits of entropy, or because prediction resistance is requested. Reseeding with fresh entropy provides prediction resistance as the new secret state is a (irreversible) function of the current secret state and some random, unknown entropy. Note that reseeding is preferred over simply instantiating a new DRBG state because if the source of entropy fails silently (supposed the bits of entropy returned are not actually random), at least the DRBG still has some randomness left over from the old entropy.
